Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-05 paper.tex
Change discussion of N^2 budget figures in Results section so that it references the tropopause height in most places rather than height levels. Also change Fig. A2 to include tropopause height.

\paragraph{0-24 hours}
The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
The 17-18-km layer was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
The layer immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary drive of the $N^2$ tendency during this period.
Although vertical turbulence acted in opposition to advection (i.e. it acted to stabilize regions that advection acted to destabilize), the magnitude of the advective tendencies was larger, particularly at the innermost radii.
The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above 17 km.
Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.

\paragraph{24-48 hours}
During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a).
These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.

Outside of the eye, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for destabilization.
Immediately below this layer was a region of increasing $N^2$, which sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
In the 16-17-km layer, a horizontally-extensive layer of decreasing $N^2$ also was forced by a combination of advection, vertical turbulence, and radiation.
The sum of advection and vertical turbulence accounts for only a portion of the decreasing $N^2$ in this layer, and actually indicates forcing for stabilization near the 50-km radius and outside of the 130-km radius.
Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization observed just below the tropopause.

The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except lower in the eyewall where the neglect of latent heating and horizontal turbulence introduces some differences.

@@

Outside of the eye, however, $N^2$ continued to increase just above the tropopause and decrease just below.
The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that the increase of $N^2$ observed in the 17-18-km layer and inside of the 80-km radius cannot be attributed to these processes, since the sum of these two terms provided forcing for destabilization.
Instead, radiation (Fig.~\ref{fig:stab-48-72}d), provided the forcing for stabilization in this region.
Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near the 18-km level.
The sum of the two terms (Fig.~\ref{fig:stab-48-72}e) indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provides the extra forcing for stabilization required to account for the observed increase in $N^2$.
Outside of the 120-km radius, the region of radiative forcing for stabilization slopes downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
The layer of decreasing $N^2$ observed near 17 km was forced primarily by vertical turbulence and radiation.
Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^2$ tendencies induced by a combination of vertical turbulence and radiation.

>>>>

\paragraph{0-24 hours}
The weakening of the lower-stratospheric $N^2$ maximum during the initial spin-up period is reflected in the total $N^2$ budget change over this time (Fig.~\ref{fig:stab-00-24}a).
The layer just above the cold-point tropopause was characterized by decreasing $N^2$ (purple shading), maximizing at the storm center.
At and immediately below the tropopause, meanwhile, saw increasing $N^2$ during this time period.
Although these tendencies extended out to the 200-km radius, they were particularly pronounced at innermost radii.
A comparison of the contributions of advection (Fig.~\ref{fig:stab-00-24}b), vertical turbulence (Fig.~\ref{fig:stab-00-24}c), and radiation (Fig.~\ref{fig:stab-00-24}d) reveals that advection was the primary driver of the $N^2$ tendency during this period, acting to stabilize near and just below the tropopause and destabilize above.
Although vertical turbulence acted in opposition to advection (i.e. it acted to stabilize regions that advection acted to destabilize), the magnitude of the advective tendencies was larger, particularly at the innermost radii.
The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-00-24}e) almost exactly replicated the static stability tendencies above the tropopause.
Radiative tendencies, meanwhile, (Fig.~\ref{fig:stab-00-24}d) acted to destabilize the layer below about 16 km and stabilize the layer between 16 and 17 km.
The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-00-24}f) reproduces the total change in $N^2$ almost exactly.

\paragraph{24-48 hours}
During the RI period, $N^2$ within the eye generally decreased above 16 km and increased below (Fig.~\ref{fig:stab-24-48}a), with the destabilization above 16 km maximizing near the level of the mean cold-point tropopause.
These tendencies at the innermost radii were driven almost entirely by advection (Fig.~\ref{fig:stab-24-48}b); vertical turbulence (Fig.~\ref{fig:stab-24-48}c) and radiation (Fig.~\ref{fig:stab-24-48}d) contributed negligibly to the static stability tendencies in this region.

Outside of the eye, the $N^2$ evolution exhibited alternating layers of positive and negative tendencies.
Near and above 18 km existed an upward-sloping region of decreasing $N^2$ that extended out to the 180-km radius.
In this region, neither vertical turbulence nor radiation exhibited negative $N^2$ tendencies; advection was the only forcing for this destabilization.
Immediately below this layer, just above the cold-point tropopause, was a region of increasing $N^2$ that sloped upward from 17 km near the 30-km radius to just below 18 km outside of the 100-km radius.
Advection and vertical turbulence both contributed to this positive $N^2$ tendency, with advection playing an important role below about 17.5 km and and turbulence playing an important role above.
The sum of advection and turbulence (Fig.~\ref{fig:stab-24-48}e) reveals two discontiguous regions of increasing $N^2$ in the 17-18-km layer rather than one contiguous region.
The addition of radiation to these two terms, however, (Fig.~\ref{fig:stab-24-48}f) provides the link between these two regions, indicating that radiation also plays a role in strengthening the stable layer just above the tropopause.
In the 16-17-km layer, just below the cold-point tropopause, a horizontally-extensive layer of destabilization also was forced by a combination of advection, vertical turbulence, and radiation.
The sum of advection and vertical turbulence accounts for only a portion of the decreasing $N^2$ in this layer, and actually indicates forcing for stabilization near the 50-km radius and outside of the 130-km radius.
Radiative tendencies overcome this forcing for stabilization in both of these regions to produce the radially-extensive region of destabilization observed just below the tropopause.

The sum of advection, vertical turbulence, and radiation (Fig.~\ref{fig:stab-24-48}f) once again closely follows the observed $N^2$ variability, except in the eyewall region, where the neglect of latent heating and horizontal turbulence introduces some differences.

@@

Outside of the eye, however, $N^2$ continued to decrease at and just below the tropopause and increase above it.
The sum of advection and vertical turbulence (Fig.~\ref{fig:stab-48-72}e) indicates that the increase of $N^2$ observed in the 17-18-km layer and inside of the 80-km radius cannot be attributed to these processes, since the sum of these two terms provided forcing for destabilization.
Instead, radiation (Fig.~\ref{fig:stab-48-72}d), provided the forcing for stabilization in this region.
Outside of the 80-km radius, both advection (Fig.~\ref{fig:stab-48-72}b) and vertical turbulence (Fig.~\ref{fig:stab-48-72}c) provided forcing for stabilization near the 18-km level.
The sum of the two terms (Fig.~\ref{fig:stab-48-72}e) indicates increasing $N^2$ near the 18-km level everywhere outside of the 80-km radius, but this stabilization is slightly weaker in the 90-120-km radial band than the observed value.
The addition of radiation (Fig.~\ref{fig:stab-48-72}f) provides the extra forcing for stabilization required to account for the observed increase in $N^2$.
Outside of the 120-km radius, the region of radiative forcing for stabilization slopes downward, and the increase in $N^2$ observed near 18 km can be explained entirely by a combination of advection and vertical turbulence.
The layer of decreasing $N^2$ observed near the tropopause was forced primarily by vertical turbulence and radiation.
Within most of this region, advection provided strong forcing for stabilization, but this forcing was outweighed by the negative $N^2$ tendencies induced by a combination of vertical turbulence and radiation.
